Wired for Success: Sweden's Electrical Innovators in the Age of Industrial Transformation

### 2023-10-12 index.qmd
change purpose

---
title: "Wired for Success: Sweden's Electrical Innovators in the Age of Industrial Transformation"
subtitle: "SEHM 2023: The application of cutting edge technology to economic history research"
author: "Jonathan Jayes  - Lund University"
title-slide-attributes:
  data-background-image: "assets/preview.png"
  data-background-size: "30%"
  data-background-opacity: "0.6"
format: 
  revealjs:
    code-overflow: wrap
    width: 1600
    height: 900
    fig-align: center
    default-image-extension: svg
    footer: "[{{< fa house >}}](https://j-jayes.github.io/Data-Visualization-in-R-Lund/)"
    slide-number: c
    code-block-bg: true
    code-block-border-left: "#31BAE9"
image: "preview_img/03-coordinate-systems-and-axes.jfif"
favicon: html/favicon.ico
---

>>>>

---
title: "Wired for Success: Sweden's Electrical Innovators in the Age of Industrial Transformation"
subtitle: "Presentation at SDU for the group working on Human Capital in the Nordic Countries"
author: "Jonathan Jayes  - Lund University"
title-slide-attributes:
  data-background-image: "assets/preview.png"
  data-background-size: "30%"
  data-background-opacity: "0.6"
format: 
  revealjs:
    code-overflow: wrap
    width: 1600
    height: 900
    fig-align: center
    default-image-extension: svg
    footer: "[{{< fa house >}}](https://interludeone.com)"
    slide-number: c
    code-block-bg: true
    code-block-border-left: "#31BAE9"
image: "preview_img/03-coordinate-systems-and-axes.jfif"
favicon: html/favicon.ico
---
